### 2017-11-01 submission/manuscript.tex
update result section name and add methods on CRC associated Genera OTU model

\textbf{\emph{Using the Whole Community Increases AUC:}}

@@

\textbf{\emph{Study Analysis Overview:}} Alpha diversity was first
assessed for differences between controls and adenoma versus cancer and
controls versus adenoma. We analyzed the data using linear mixed-effect
models, and relative risk. Beta-diversity was then assessed for each
inidividual study. Next, four specific CRC-associated genera
(\emph{Fusobacterium}, \emph{Parvimonas}, \emph{Peptostreptococcus}, and
\emph{Porphyromonas}) were assessed for differences in relative risk. We
then built Random Forest models based on all genera or the select
CRC-associated genera. The models were trained on one study then tested
on the remaining studies for every study. The data was split between
feces and tissue samples. Within the tissue groups the data was further
divided between matched and unmatched tissue samples. Both prediction
for adenoma and carcinoma were tested. This same approach was then
applied at the OTU level with the exception that instead of testing on
the other studies a 10-fold cross validation was utilized and 100
different models were created based on random 80/20 splitting of the
data to generate a range of expected AUCs. The power of each study was
assessed for and effect size ranging from 1\% to 30\%. An estimated
sample n for these effect sizes was also generated based on 80\% power.

>>>>

\textbf{\emph{Using the Whole Community Increases Model AUC:}}

@@

\textbf{\emph{Study Analysis Overview:}} Alpha diversity was first
assessed for differences between controls and adenoma versus cancer and
controls versus adenoma. We analyzed the data using linear mixed-effect
models, and relative risk. Beta-diversity was then assessed for each
inidividual study. Next, four specific CRC-associated genera
(\emph{Fusobacterium}, \emph{Parvimonas}, \emph{Peptostreptococcus}, and
\emph{Porphyromonas}) were assessed for differences in relative risk. We
then built Random Forest models based on all genera or the select
CRC-associated genera. The models were trained on one study then tested
on the remaining studies for every study. The data was split between
feces and tissue samples. Within the tissue groups the data was further
divided between matched and unmatched tissue samples. Both prediction
for adenoma and carcinoma were tested. This same approach was then
applied at the OTU level with the exception that instead of testing on
the other studies a 10-fold cross validation was utilized and 100
different models were created based on random 80/20 splitting of the
data to generate a range of expected AUCs. For OTU based models the CRC
Associated Genera included all OTUs that had a taxonomic classification
to \emph{Fusobacterium}, \emph{Parvimonas}, \emph{Peptostreptococcus},
or \emph{Porphyromonas}. The power of each study was assessed for and
effect size ranging from 1\% to 30\%. An estimated sample n for these
effect sizes was also generated based on 80\% power.
